```{r data_generation_diagnostics, echo=FALSE, results='hide'}
library(exams)

# True and False statements for each diagnostic plot

# Residuals vs Fitted statements
residuals_fitted_true <- c("The Residuals vs Fitted plot checks for non-linearity in the data.",
                           "A Residuals vs Fitted plot helps detect if residuals have unequal variance (heteroscedasticity).")
residuals_fitted_false <- c("The Residuals vs Fitted plot checks for the normality of residuals.",
                            "In the Residuals vs Fitted plot, points should form a straight diagonal line.")

# Normal Q-Q statements
qqplot_true <- c("The Normal Q-Q plot checks whether residuals follow a normal distribution.",
                 "In the Normal Q-Q plot, points should ideally lie on a straight diagonal line.")
qqplot_false <- c("The Normal Q-Q plot checks for homoscedasticity (constant variance) of residuals.",
                  "The Normal Q-Q plot is used to check for influential points in the dataset.")

# Scale-Location (Spread-Location) statements
scale_location_true <- c("The Scale-Location plot checks whether residuals have constant variance across fitted values.",
                         "A Scale-Location plot is used to detect heteroscedasticity in the data.")
scale_location_false <- c("The Scale-Location plot checks for linearity in the relationship between predictors and outcome.",
                          "In the Scale-Location plot, points should follow a straight diagonal line to confirm normality.")

# Residuals vs Leverage statements
residuals_leverage_true <- c("The Residuals vs Leverage plot helps identify influential observations that can affect the model.",
                             "High leverage points in the Residuals vs Leverage plot can indicate potential outliers.")
residuals_leverage_false <- c("The Residuals vs Leverage plot checks for normality of residuals.",
                              "In the Residuals vs Leverage plot, points should form a diagonal line to ensure linearity.")

# Randomly select true or false statements for each diagnostic plot
questions <- c(sample(c(residuals_fitted_true, residuals_fitted_false), 1),
               sample(c(qqplot_true, qqplot_false), 1),
               sample(c(scale_location_true, scale_location_false), 1),
               sample(c(residuals_leverage_true, residuals_leverage_false), 1))

# Determine the correct solutions (TRUE for correct statements, FALSE for incorrect ones)
solutions <- c(questions[1] %in% residuals_fitted_true,
               questions[2] %in% qqplot_true,
               questions[3] %in% scale_location_true,
               questions[4] %in% residuals_leverage_true)

# Explanations for each question
explanations <- character(4)
explanations[1] <- ifelse(solutions[1], "The Residuals vs Fitted plot checks for non-linearity and heteroscedasticity.", 
                          "The Residuals vs Fitted plot does not check for normality; it checks for non-linearity and unequal variance.")
explanations[2] <- ifelse(solutions[2], "The Normal Q-Q plot is used to assess the normality of residuals.", 
                          "The Normal Q-Q plot does not assess homoscedasticity or influential points; it checks for normality.")
explanations[3] <- ifelse(solutions[3], "The Scale-Location plot helps detect heteroscedasticity in the data.", 
                          "The Scale-Location plot is used to check for constant variance, not linearity or normality.")
explanations[4] <- ifelse(solutions[4], "The Residuals vs Leverage plot helps identify influential points that could distort the model.", 
                          "The Residuals vs Leverage plot is used to find influential points, not to check for normality or linearity.")

# Randomize order of questions
Order <- sample(1:4)
questions <- questions[Order]
solutions <- solutions[Order]
explanations <- explanations[Order]

```

Question
========

Which of the following statements correctly describes one of the diagnostic plots used to assess a linear model?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(questions, markup = "markdown")
```

Solution
========

Here are the diagnostic plots and their purposes:

    Residuals vs Fitted: Checks for non-linearity and heteroscedasticity.
    Normal Q-Q: Checks whether residuals are normally distributed.
    Scale-Location (Spread-Location): Checks for constant variance of residuals (homoscedasticity).
    Residuals vs Leverage: Identifies influential observations (high leverage points) that can affect the model.
  
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(mchoice2text(solutions, markup="markdown"), explanations, markup = "markdown")

```

Meta-information
================
  
extype: mchoice
exsolution: `r mchoice2string(solutions)`
exname: Multiple Choice
